---
title: "Linear Regression_Class Assesment_Saiifi Haider-PGA19"
author: "Saiifi Haider"
date: "December 14, 2021"
output:
pdf_document: default
html_document: default
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Reading the Data-set

```{r}
train= read.csv("D:/Imarticus/Exam_Assesment_section/R_Programming/Linear_Regression/Dataset/PropertyTrainData.csv")
test = read.csv("D:/Imarticus/Exam_Assesment_section/R_Programming/Linear_Regression/Dataset/PropertyTestData.csv")
```

#### Concatinating train and test data.

```{r}
df = rbind(train,test)
```

#### Viewing the data
```{r}
View(df)
```

#### Basic information about the data

```{r}
str(df)
```

```{r}
summary(df)
```

#### Checking the null values

```{r}
sum(is.na(df))
```

## Exploratory Data Analysis

#### correlation matrix

```{r}
cor_mat = cor(df, method = 'pearson', use = 'complete.obs')
cor_mat
```

#### Plot the correlation

```{r}
library(DataExplorer)
plot_correlation(na.omit(df), maxcat = 5L)
```

#### Pairplot

```{r}
library(ggplot2)
library(GGally)
ggpairs(df, columns= c('Price','Sea','Area','Elevation','Sewer','Days','Flood','Distance'))
```

#### Boxplot

```{r}
par(mfrow=c(2,4))
with(df, boxplot(Price))      
with(df, boxplot(Sea))
with(df, boxplot(Area))
with(df, boxplot(Elevation))
with(df, boxplot(Sewer))
with(df, boxplot(Days))
with(df, boxplot(Flood))
with(df, boxplot(Distance))
```

#### Remove the ouliers from price and sewer

```{r}
box_plot_price<-ggplot(data=df, aes(y = Price)) 
box_plot_price+ geom_boxplot(outlier.shape = NA) +
  coord_cartesian(ylim =  c(1, 35))
```

```{r}
box_plot_sewer<-ggplot(data=df, aes(y = Sewer)) 
box_plot_sewer+ geom_boxplot(outlier.shape = NA) +
  coord_cartesian(ylim =  c(0,9000))
```

#### plot the scatter plot

```{r}
qplot(Area, Price, data = df)
qplot(Elevation, Price, data = df)
qplot(Sewer, Price, data = df)
qplot(Days, Price, data = df)
qplot(Distance, Price, data= df)
```

#### Feature Scaling

```{r}
train[,2] = scale(train[,2])     #select only sea column
test[,2] = scale(test[,2])

train[,7] = scale(train[,7])     #select only Flood column
test[,7] = scale(test[,7])
```

#### Build the model

```{r}
lm_model <- lm(Price ~., data = train)
summary(lm_model)
```

#### Predict the value

```{r}
lm_pred <- predict(lm_model, newdata = test)
lm_pred
head(test$Price)
```

#### Cost function

```{r}
resids <- data.frame(test$Price, lm_pred,
                     residuals= test$Price - lm_pred)
head(resids, 10)
```

#### Evaluation matrix

```{r}
mse_lm <- mean((resids$residuals)^2, na.rm = T)
head(mse_lm, 5)

```

```{r}
rmse_lm <- sqrt(mse_lm)
rmse_lm
```
